WORCS: A Workflow for Open Reproducible Code in Science

### 2020-10-27 paper/reviews_ds.Rmd
Fix backticks

* Overall Impression: Weak
* Suggested Decision: Reject
* Technical Quality of the paper: Good
* Presentation: Good
* Reviewer`s confidence: High
* Significance: High significance
* Background: Reasonable
* Novelty: Limited novelty
* Data availability: All used and produced data (if any) are FAIR and openly available in established data repositories
* Length of the manuscript: The length of this manuscript is about right

@@

* Overall Impression: Good
* Suggested Decision: Accept
* Technical Quality of the paper: Good
* Presentation: Good
* Reviewer`s confidence: Medium
* Significance: High significance
* Background: Reasonable
* Novelty: Limited novelty
* Data availability: With exceptions that are admissible according to the data availability guidelines, all used and produced data are FAIR and openly available in established data repositories
* Length of the manuscript: The length of this manuscript is about right

@@

* Overall Impression: Weak
* Suggested Decision: Reject
* Technical Quality of the paper: Average
* Presentation: Good
* Reviewer`s confidence: High
* Significance: High significance
* Background: Reasonable
* Novelty: Limited novelty
* Data availability: All used and produced data (if any) are FAIR and openly available in established data repositories
* Length of the manuscript: The length of this manuscript is about right

@@

* Overall Impression: Good
* Suggested Decision: Accept
* Technical Quality of the paper: Excellent
* Presentation: Good
* Reviewer`s confidence: Medium
* Significance: Moderate significance
* Background: Reasonable
* Novelty: Limited novelty
* Data availability: All used and produced data (if any) are FAIR and openly available in established data repositories
* Length of the manuscript: The length of this manuscript is about right

>>>>

* Overall Impression: Weak
* Suggested Decision: Reject
* Technical Quality of the paper: Good
* Presentation: Good
* Reviewer's confidence: High
* Significance: High significance
* Background: Reasonable
* Novelty: Limited novelty
* Data availability: All used and produced data (if any) are FAIR and openly available in established data repositories
* Length of the manuscript: The length of this manuscript is about right

@@

* Overall Impression: Good
* Suggested Decision: Accept
* Technical Quality of the paper: Good
* Presentation: Good
* Reviewer's confidence: Medium
* Significance: High significance
* Background: Reasonable
* Novelty: Limited novelty
* Data availability: With exceptions that are admissible according to the data availability guidelines, all used and produced data are FAIR and openly available in established data repositories
* Length of the manuscript: The length of this manuscript is about right

@@

* Overall Impression: Weak
* Suggested Decision: Reject
* Technical Quality of the paper: Average
* Presentation: Good
* Reviewer's confidence: High
* Significance: High significance
* Background: Reasonable
* Novelty: Limited novelty
* Data availability: All used and produced data (if any) are FAIR and openly available in established data repositories
* Length of the manuscript: The length of this manuscript is about right

@@

* Overall Impression: Good
* Suggested Decision: Accept
* Technical Quality of the paper: Excellent
* Presentation: Good
* Reviewer's confidence: Medium
* Significance: Moderate significance
* Background: Reasonable
* Novelty: Limited novelty
* Data availability: All used and produced data (if any) are FAIR and openly available in established data repositories
* Length of the manuscript: The length of this manuscript is about right
